Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/results-devices.tex
oops

To preserve data independence, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$). Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors. As a result, we can conclude that in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible. Similarly, the entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.

>>>>

To ensure independence of observations, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$). Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors. As a result, we can conclude that in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible. Similarly, the entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.
